Think deep for reef resilience

### 2025-08-06 paper/paper_draft.qmd
Add details on how DHWs were calculated from functions and [skirving]
Added details from model functions, referring to Skirving et al. (2020), about how DHW were calculated from SST data.

@ConnectedSystems I'm unsure of where the repository link/citation to code fits into the paper best

The spatial extent of the GBR reefs represented in this investigation follows the reef
definitions available via the Great Barrier Reef Marine Park Authority [@greatba2022]. In
total, the dataset represents 3806 reef areas across the GBR marine park. Reefs that are
outside the GBRMPA management areas or are not associated with a GBRMPA reefal bioregion
were removed from the investigation, leaving 3531 reefs. Annually and spatially averaged
Degree Heating Week (DHW) data were used to represent future thermal stress at each reef
location.

@@

Maximum monthly mean DHW levels were calculated from the SST data following NOAA methodology
[@liu2017; @skirving2020], from which maximum yearly DHWs were determined.
**\[TI: Could you confirm the above is described correctly?\]**

>>>>

The spatial extent of the GBR reefs represented in this investigation follows the reef
definitions available via the Great Barrier Reef Marine Park Authority [@greatba2022]. In
total, the dataset represents 3806 reef areas across the GBR marine park. Reefs that are
outside the GBRMPA management areas or are not associated with a GBRMPA reefal bioregion
were removed from the investigation, leaving 3531 reefs. Annually and spatially averaged
Degree Heating Week (DHW) data were used to represent future thermal stress at each reef
location. Code used to calculate DHW data and perform analyses involved in this
investigation can be found at **insert repo citation**.

@@

Maximum monthly mean DHW levels were calculated from the SST data following NOAA methodology
[@liu2017; @skirving2020]. For each pixel of SST data, the monthly mean SST climatoloy (MM)
was calculated as the mean SST for each month over 1985 to 2012, adjusted to centre at year
1988.2857 (see Skirving et al. [-@skirving2020]). The "HotSpot SST Anomaly" [@skirving2020]
was calculated as the difference between daily SST values and the maxmimum of a pixel's MM
climatology (maximum monthly mean). DHW values are then calculated as the 12-week rolling
sum of positive HotSpot SST Anomaly values for a pixel. 
**\[TI: Could you confirm the above is described correctly?\]**
